Effects of the body force on the pedestrian and the evacuation dynamics

### 2020-02-07 paper.tex
pequeñas correcciones en resumen

The Social Force Model (SFM) is a suitable model for describing crowd behaviors.
This research analyzes the role of the body force in the original SFM. 
We focused on the parameter associated to the body stiffness ($k_n$) and its impact on
the pedestrian dynamics for two different geometries: bottlenecks and corridors.
Increasing $k_n$ produces opposite effects on either geometry: an increase of the 
crowd velocity for bottlenecks, and a decrease for corridors. 
The former reflects the fact that stiffness reduces the overlaps and the sliding friction
among pedestrians. This reduces the number of blocking cluster close
to the exit door.  The corridor, instead, tights the pedestrians into a lattice-like configuration
due to space limitations. The friction interaction with the walls determine the velocity
of the whole crowd along the corridor. 
Additionally, the corridor geometry experiences a flux slowing down for very crowded environments,
as observed in many real-life situations.
We also explored the dimensionless parameters that arise from the reduced-in-units equation 
of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.

>>>>

The Social Force Model (SFM) is a suitable model for describing crowd behaviors.
This research analyzes the role of the body force in the original SFM.
We focused on the parameter associated with the body stiffness ($k_n$) and its impact on the pedestrian
dynamics for two different geometries: bottlenecks and corridors.
Increasing $k_n$ produces opposite effects on either geometry: an increase of the crowd velocity 
for bottlenecks, and a decrease for corridors. 
The former reflects the fact that the stiffness reduces
the overlaps and the sliding friction among pedestrians. 
This phenomenon reduces the number of blocking clusters close to the exit door. 
The corridor, instead, tights the pedestrians into a lattice-like configuration due to space limitations.
The friction interaction with the walls determines the velocity of the whole crowd along the corridor.
Additionally, the corridor geometry experiences a flux slowing down for very
crowded environments, as observed in many real-life situations.
We also explored the dimensionless parameters that arose from the reduced-in-units
equation of motion and tuned them to reproduce the qualitative behavior of the empirical fundamental diagram.
